scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Remove suggestion about skimage.viewer
That module definitely needs some love. I don't think it's ready for
mention in a publication.
Various typo/wording fixes

speak about skimage's visualizer as well?

@@

The modularity of the Scientific Python ecosystem may look
confusing at first sight. Nevertheless, core modules of this ecosystem
are almost perfectly compatible, thanks to the shared use of NumPy arrays
and common development practices, although they are developed in parallel
by different teams.

@@

The success of a software package aimed at end-users is strongly
correlated to the quality of its documentation (find citation).
\texttt{scikit-image} users have access to different kinds of
documentation. Functions of the API (define API here or above) are all
documented using the same standard~\citep{Pawlik2015} as other major
Scientific Python packages. The standard include a description of all
input and output variables and their data type, together with
explainations on what the function does and how to use it. Functions
documentation is accessed either online, or within the development
environment (IPython, Spyder, Jupyter Notebook...).

@@

In addition, a popular documentation tool is the graphical gallery of
examples (\url{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
The principle of the gallery is to accelerate the learning curve of image
processing, by showcasing graphical examples of image processing
operations. Such examples are organized as an array of thumbnails with a
short title (see Fig.~\ref{fig:gallery} left). Thumbnails are links to
the webpage of the corresponding example, which features a mini-tutorial
on the image processing method, the code needed to run the example and
the figure generated by the example. Since the graphical gallery is an
efficient way to inform users about the features of
\texttt{scikit-image}, every new feature integrated in the package must
include an example for the gallery.

>>>>

@@

The modularity of the Scientific Python ecosystem may look
confusing at first sight. Nevertheless, core modules of this ecosystem
are almost perfectly compatible, thanks to the shared use of NumPy arrays
and common development practices (although they are developed in parallel
by different teams).

@@

The success of a software package aimed at end-users is strongly
correlated to the quality of its documentation (find citation).
\texttt{scikit-image} users have access to different kinds of
documentation. Functions of the API (define API here or above) are all
documented using the same standard~\citep{Pawlik2015} as other major
Scientific Python packages. The standard include a description of all
input and output variables and their data type, together with
explanations on what the function does and how to use it. Function
documentation is accessed either online, or within the development
environment (IPython, Spyder, Jupyter Notebook...).

@@

In addition, a popular documentation tool is the graphical gallery of
examples (\url{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
The principle of the gallery is to accelerate the learning curve of image
processing, by showcasing graphical examples of image processing
operations. Such examples are organized as an array of thumbnails with a
short title (see Fig.~\ref{fig:gallery} left). These thumbnails link to
the webpage of the corresponding example, which features a mini-tutorial
on the image processing method, the code needed to run the example and
the figure generated by the example. Since the graphical gallery is an
efficient way to inform users about the features of
\texttt{scikit-image}, every new feature integrated in the package must
include an example for the gallery.
